%%%%%%%%%%%%%%%%%
% This is an sample CV template created using altacv.cls
% (v1.1.4, 27 July 2018) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
% 
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

%% If you are using \orcid or academicons
%% icons, make sure you have the academicons 
%% option here, and compile with XeLaTeX
%% or LuaLaTeX.
% \documentclass[10pt,a4paper,academicons]{altacv}

%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}


\documentclass[10pt,a4paper]{altacv}
% \usepackage[most]{tcolorbox}

\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!70,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=5pt,
    arc=0pt,outer arc=0pt,
    }


% Change the page layout if you need to
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=.75cm,bottom=1.25cm,footskip=2\baselineskip}

% Change the font if you want to.

% If using pdflatex:
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[default]{lato}


\definecolor{Navy}{HTML}{002f45}
\definecolor{SlateGrey}{HTML}{000000}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{Navy}
\colorlet{accent}{Navy}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{SlateGrey}


\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\addbibresource{sample.bib}

\usepackage[colorlinks]{hyperref}

\begin{document}

\name{MEHUL GUPTA}


\personalinfo{\colorbox{blue!65!green!50!}
{
    \email{mehulgupta85@gmail.com}
    \hspace{20px}
    \phone{+91-9650292077}    %\newcommand*{\dateofbirth}[1]{}
    \hspace{20px}
    \location{Delhi, India}
    \hspace{20px}
    \linkedin{www.linkedin.com/in/mehulguptasmh}
    \hspace{20px}
}}

% \end{tcolorbox}

%% Make the header extend all the way to the right, if you want. 
\begin{fullwidth}
\makecvheader
\end{fullwidth}

\cvsection[page1sidebar]{Experience}

\cvevent{\textbf{Zenon.AI}}{Senior Analytics Specialists}{October 2021  -- Present}{Noida (remote)}

\textbf{Lead analyst for Wealth Management and Analytics team for a Major International Investment Bank}
\begin{itemize}
    \item Provide support in the management of a portfolio of size over \$600 Billion in AUM with the developed reporting pipeline, saving over 90\% in lead times.
    \item Developed near-real-time New Asset forecasting tools for the full year, helping take strategic decisions faster and save over 99\% in terms of man-hours.
\end{itemize}

\vspace{5px}

\textbf{Data Scientist(NLP) solutions for a Major International Fintech}
\begin{itemize}
    \item Developed a solution for extracting key information from contract documents using BERT-based NER/TC models, and Co-Reference resolution to name a few.
    \item Developing solution for decomposing complex sentences into simpler sentences using different approaches such as Knowledge graphs, Generative Models, etc.
\end{itemize}

\vspace{5px}


\cvevent{\textbf{Paytm Insurance }}{Senior Associate}{July 2021  -- October 2021}{Noida, UP}

\textbf{Lead analyst for Digital Marketing team for Insurance Business}
\begin{itemize}
    \item Developed pipelines and models for industry-standard key metrics, essential for strategic and effective campaign management over various channels.
    \item Developed methodologies for cohort identification from customers population to target for up-sell/X-sell.
\end{itemize}

\vspace{5px}

\cvevent{\textbf{Cognitio Analyitics Pvt Ltd }}{Senior Analyst}{July 2019  -- July 2021}{Gurgaon, Haryana}

\textbf{Enhancing the delivery of healthcare services for US-based self-insured employers}
\begin{itemize}
    \item Increasing domestic utilization by employees for a US-based national-level hospital chain, creating additional savings of over USD \$40 Million per year.
    \item Quantify impact created by the third-party service provider for services rendered and benchmarking against SLAs, helping save over \$30 Million for service-related costs. 
\end{itemize}

\vspace{5px}

\textbf{Churn model for customer default for US-based nonstandard Auto Insurance client}
\begin{itemize}
    \item Developed model to identify customers with a higher risk of defaulting based on factors such as customer income, previous default status, etc., saving over USD \$2 Million and improving the overall customer journey.
\end{itemize}

\vspace{5px}

\textbf{Product Development.}
\begin{itemize}
    \item Developed \emph{custom Process Mining tool} with capabilities of providing visualizations on par with BI Tools like Tableau with support of multiple data connectors and file structures.
    \item \emph{Developed centralized platform} for providing standardized as well as customized solutions for clients including data management, custom analysis, reporting solutions, data quality maintenance, etc.
\end{itemize}

\vspace{10px}




\medskip


\end{document}
